Collocated Deduplication with Fault Isolation for Virtual Machine Snapshot Backup

### 2013-05-29 snapshot_system/design1.tex

%\subsection{ Snapshot management}
The virtual device driver uses a bitmap to track the changes that have been made to virtual disk.
Every bit in the bitmap represents a fix-sized (2MB) region called \textit{segment}, indicates whether the segment
is modified since last backup. Hence we could treat segment as the basic unit in snapshot backup similar to
file in normal backup: a snapshot could share a segment with previous snapshot it is not changed. 
Moreover, we break segments into var-sized chunks (average 4KB) using content-based chunking algorithm,
which brings the opportunity of fine-grained deduplication by
allowing data sharing between segments.
The representation of each snapshot has  a two-level index data structure. 
%in the form of a hierarchical directed acyclic graph as shown in Figure \ref{fig:snapshot}.
The snapshot meta data (called snapshot receipe) contains a list of segments, each of which contains segment 
meatdata of its chunks (called segment receipe).

@@

@@

\begin{figure}[htbp]
  \centering
  %\epsfig{file=images/arch.eps, height=2in, width=2.66in}
  \epsfig{file=images/arch.eps, width=3.9in}
  \caption{Snapshot backup architecture of each node.}
  \label{fig:arch}
\end{figure}

>>>>

%\subsection{ Snapshot management}
The virtual device driver uses a bitmap to track the changes that have been made to virtual disk.
Every bit in the bitmap represents a fix-sized (2MB) region called \textit{segment}, indicates whether the segment
is modified since last backup. Hence we could treat segment as the basic unit in snapshot backup similar to
file in normal backup: a snapshot could share a segment with previous snapshot it is not changed. 
Moreover, we break segments into var-sized chunks (average 4KB) using content-based chunking algorithm,
which brings the opportunity of fine-grained deduplication by
allowing data sharing between segments.

The representation of each snapshot has  a two-level index data structure. 
%in the form of a hierarchical directed acyclic graph as shown in Figure \ref{fig:snapshot}.
The snapshot meta data (called snapshot receipe) contains a list of segments, each of which contains segment 
meatdata of its chunks (called segment receipe).

@@

\begin{figure}[htbp]
  \centering
  \epsfig{file=images/snapshot_representation.pdf, width=3.7in}
  \caption{An example of snapshot representation.}
  \label{fig:snapshot}
\end{figure}
As a result, the representation of each snapshot is designed as a two-level index data structure 
in the form of a hierarchical directed acyclic graph as shown in Figure \ref{fig:snapshot}.
A snapshot recipe contains a list of segments, each of which is represented as a segment recipe
that holds the meatdata of its chunks. We choose this two-level structure because in practice we
observe that during each backup period only a small amount of VM data are added or modified. 
As the result, even the metadata of two snapshots can be highly similar, 
thus aggregating a large number of chunks as one segment can significantly reduce the space cost of snapshot metadata.
Furthermore, instead of using variables-sized segments, we use a dirty bit to capture the change status of fix-sized
segments which greatly ease the segment-level deduplication.

@@

\begin{figure}[htbp]
  \centering
  \epsfig{file=images/arch.pdf, width=3.9in}
  \caption{Snapshot backup architecture of each node.}
  \label{fig:arch}
\end{figure}

### 2013-05-29 snapshot_system/snapshot.tex

\item \textbf{Chunk-level fine-grain nearby duplicate detection.}

The best deduplication uses a nonuniform chunk size 
in the average of 4K or 8K~\cite{??}.
Thus the second-level inner-VM deduplication is to assess in this
level, but only for those dirty  segments. 
We load the fingerprints of block chunks of the corresponding segment from the
parent for a comparisons and compare near-by fingerprint matching within this segement.
The amount of memory for maintaining those fingerprints  is small.
For example, with a 2MB segment, there are about 500 fingerprints to compare.

@@

[Describe the dedup efficiency model in detail]
Let $S_c$ be the total number of FPs in CDS, $S_g$ be the total number of FPs in global index, $F$ be the size of a FP, $N$ be the number of nodes in the cluster, $m$ be the memory on each node that are used by CDS, $D$ be the amount of data on each node, and $B$ be the average block size. The deduplication efficiency will be:
\begin{equation}
  E = (S_c / S_g)^{1-\alpha}
\end{equation}
The $S_c$ and $S_g$ can be expressed as:
\begin{equation}
S_c = N*m/F, S_g = N*D/B
\end{equation}
By replacing $S_c$ and $S_g$ in the first formula, we have:
\begin{equation}
  E = (\frac{m*B}{F*D})^{1-\alpha}
\end{equation}

>>>>

\item \textbf{Chunk-level fine-grain nearby duplicate detection.}
The best deduplication uses a nonuniform chunk size 
in the average of 4K or 8K~\cite{??}.
Thus the second-level inner-VM deduplication is to assess in this
level, but only for those dirty  segments. 
We load the fingerprints of block chunks of the corresponding segment from the
parent for a comparisons and compare near-by fingerprint matching within this segement.
The amount of memory for maintaining those fingerprints  is small.
For example, with a 2MB segment, there are about 500 fingerprints to compare.

@@

[Describe the dedup efficiency model in detail]
Let $S_c$ be the total number of FPs in CDS, $S_g$ be the total number of FPs in global index, $F$ be the size of a FP, $N$ be the number of nodes in the cluster, $m$ be the memory on each node that are used by CDS, $D$ be the amount of data on each node, and $B$ be the average block size. The deduplication efficiency will be:
\begin{equation}
  E = (S_c / S_g)^{1-\alpha}
\end{equation}
{\bf How this is derived?} 
The $S_c$ and $S_g$ can be expressed as:
\begin{equation}
S_c = N*m/F, S_g = N*D/B
\end{equation}
By replacing $S_c$ and $S_g$ in the first formula, we have:
\begin{equation}
  E = (\frac{m*B}{F*D})^{1-\alpha}
\end{equation}
